Type Visualization for R

### 2020-06-20 paper/main.tex
paper: Typos

\author{Roy G. Biv\thanks{e-mail: roy.g.biv@aol.com} %
\and Ed Grimley\thanks{e-mail:ed.grimley@aol.com} %
\and Martha Stewart\thanks{e-mail:martha.stewart@marthastewart.com}}
\affiliation{\scriptsize Northeastern University}

@@

On the frontend, state management, interactivity,
and DOM manipulation is all done within the Vue framework.
This is in contrast with many web-based visualizations
that use D3 for DOM manipulation.
We chose this setup because of the many different
individual components whose state must be kept
sychronized.
This includes not only the visualizations, but also
user interface elements like the autocomplete search bar.
In our experience, Vue's model of reactivity is
more successful at maintaining consistency across the
entire system than using D3 and vanilla JavaScript.
While {\sc TypeVis} does not use D3 for DOM manipulation,
it still does use D3 for other visualization-related
computations.

Our backend is a Node.js application that serves
JSON in a standard REST-style architecture.
Data is stored in a SQLite database that has been
indexed to achieve lookups as fast as possible.
To avoid execessive memory consumption and speed up computations,
clients query data from the server on an as-needed basis.
Thus, a stable network connection is required for
real-time interaction.

@@

We have presented {\sc TypeVis}, an interactive visualization
of run-time type information for R.
It supports real-time exploration of a dataset of
execution traces from a large corpus of R packages.
To narrow the data under consideration,
{\sc TypeVis} provides facilities for filtering
and searching.
Type signatures are represented as flows travesing across
each argument type and return type in sequence.
Flow widths are proportional to how often
that type signature was seen during the dynamic analysis.
Interactions provide additional details and
assist users in comprehension and navigation.

>>>>

\author{Cameron Moy\thanks{camoy@ccs.neu.edu}
\and Julia Belyakova\thanks{belyakovay@ccs.neu.edu}}
\affiliation{\scriptsize Northeastern University}

@@

On the frontend, state management, interactivity,
and DOM manipulation is all done within the Vue framework.
This is in contrast with many web-based visualizations
that use D3 for DOM manipulation.
We chose this setup because of the many different
individual components whose state must be kept
synchronized.
This includes not only the visualizations, but also
user interface elements like the autocomplete search bar.
In our experience, Vue's model of reactivity is
more successful at maintaining consistency across the
entire system than using D3 and vanilla JavaScript.
While {\sc TypeVis} does not use D3 for DOM manipulation,
it still does use D3 for other visualization-related
computations.

Our backend is a Node.js application that serves
JSON in a standard REST-style architecture.
Data is stored in a SQLite database that has been
indexed to achieve lookups as fast as possible.
To avoid excessive memory consumption and speed up computations,
clients query data from the server on an as-needed basis.
Thus, a stable network connection is required for
real-time interaction.

@@

We have presented {\sc TypeVis}, an interactive visualization
of run-time type information for R.
It supports real-time exploration of a dataset of
execution traces from a large corpus of R packages.
To narrow the data under consideration,
{\sc TypeVis} provides facilities for filtering
and searching.
Type signatures are represented as flows traversing across
each argument type and return type in sequence.
Flow widths are proportional to how often
that type signature was seen during the dynamic analysis.
Interactions provide additional details and
assist users in comprehension and navigation.
